\chapter*{ABSTRACT}

With the rapid development of generative artificial intelligence, AI-generated content has been widely applied to image synthesis, video generation, digital human animation, and intelligent media creation. However, the increasing realism and accessibility of these technologies have also introduced security challenges, including forged content dissemination, unsafe media generation, identity misuse, and growing pressure on content moderation. Focusing on the security risks of AI-generated content in practical scenarios, this thesis studies fake content detection and unsafe content recognition for images and videos, and further designs a multimodal content security detection and analysis platform.

This thesis first reviews the development of AIGC generation technologies, deepfake-related manipulation methods, and existing security detection approaches, and analyzes their differences in detection targets, generalization ability, deployment cost, and engineering adaptability. On this basis, a three-layer system architecture is designed, consisting of a front-end presentation layer, a back-end proxy layer, and a model inference layer. By integrating locally deployed detection models with external multimodal review APIs, the platform forms a unified workflow covering content input, security analysis, risk grading, and visualized result presentation. The system supports image and video upload, URL-based input, fake content identification, unsafe content review, result visualization, and output management, which provides an effective foundation for later experiments, sample construction, and application verification.

In the experimental analysis, the thesis verifies image fake detection, video content analysis, unsafe content review, and platform usability according to the current implementation progress. The results and discussion summarize the applicable scenarios of local models and external APIs in different tasks. Therefore, the work not only reflects the engineering practice of building a deployable tool, but also provides a practical reference for AIGC content governance and multimodal security research.

\vspace{1em}
\noindent\textbf{Key words:} AIGC security, multimodal detection, fake content detection, unsafe content recognition, content security platform
