\begin{thebibliography}{99}
\phantomsection
\addcontentsline{toc}{section}{参考文献}

\bibitem{ref1}
GOODFELLOW I, POUGET-ABADIE J, MIRZA M, et al. Generative adversarial nets[C]//Advances in Neural Information Processing Systems 27. Red Hook, NY: Curran Associates, 2014: 2672-2680.

\bibitem{ref2}
KARRAS T, AILA T, LAINE S, et al. Progressive growing of GANs for improved quality, stability, and variation[C]//International Conference on Learning Representations. Vancouver: OpenReview.net, 2018.

\bibitem{ref3}
KARRAS T, LAINE S, AILA T. A style-based generator architecture for generative adversarial networks[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. Long Beach: IEEE, 2019: 4401-4410.

\bibitem{ref4}
HO J, JAIN A N, ABBEEL P. Denoising diffusion probabilistic models[C]//Advances in Neural Information Processing Systems 33. Red Hook, NY: Curran Associates, 2020: 6840-6851.

\bibitem{ref5}
SONG Y, SOHL-DICKSTEIN J, KINGMA D P, et al. Score-based generative modeling through stochastic differential equations[C]//International Conference on Learning Representations. Virtual: OpenReview.net, 2021.

\bibitem{ref6}
ROMBACH R, BLATTMANN A, LORENZ D, et al. High-resolution image synthesis with latent diffusion models[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. New Orleans: IEEE, 2022: 10684-10695.

\bibitem{ref7}
SAHARIA C, CHAN W, CHANG H, et al. Photorealistic text-to-image diffusion models with deep language understanding[C]//Advances in Neural Information Processing Systems 35. Red Hook, NY: Curran Associates, 2022: 36479-36494.

\bibitem{ref8}
RADFORD A, KIM J W, HALLACY C, et al. Learning transferable visual models from natural language supervision[C]//Proceedings of the 38th International Conference on Machine Learning. New York: PMLR, 2021: 8748-8763.

\bibitem{ref9}
WANG S Y, WANG O, ZHANG R, et al. CNN-generated images are surprisingly easy to spot... for now[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. Seattle: IEEE, 2020: 8695-8704.

\bibitem{ref10}
OJHA U, LI Y, LEE Y J. Towards universal fake image detectors that generalize across generative models[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. Vancouver: IEEE, 2023: 24480-24489.

\bibitem{ref11}
TAN C, ZHAO Y, WEI S, et al. Learning on gradients: generalized artifacts representation for GAN-generated images detection[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. Vancouver: IEEE, 2023: 12105-12114.

\bibitem{ref12}
CHEN B, ZENG J, YANG J, et al. DRCT: Diffusion reconstruction contrastive training towards universal detection of diffusion generated images[C]//Proceedings of the 41st International Conference on Machine Learning. New York: PMLR, 2024: 7621-7639.

\bibitem{ref13}
ROSSLER A, COZZOLINO D, VERDOLIVA L, et al. FaceForensics++: Learning to detect manipulated facial images[C]//Proceedings of the IEEE/CVF International Conference on Computer Vision. Seoul: IEEE, 2019: 1-11.

\bibitem{ref14}
LI Y, LYU S. Exposing DeepFake videos by detecting face warping artifacts[C]//Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition Workshops. Long Beach: IEEE, 2019: 46-52.

\bibitem{ref15}
CORVI R, COZZOLINO D, ZINGARINI G, et al. On the detection of synthetic images generated by diffusion models[C]//ICASSP 2023 - 2023 IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP). Rhodes Island: IEEE, 2023: 1-5.

\bibitem{ref16}
ZHENG C, SUO R, LIN C, et al. D3: Training-free AI-generated video detection using second-order features[C]//Proceedings of the IEEE/CVF International Conference on Computer Vision. Honolulu: IEEE, 2025: 12852-12862.

\bibitem{ref17}
MIAO Y, ZHU Y, YU L, et al. T2VSafetyBench: Evaluating the safety of text-to-video generative models[C]//Advances in Neural Information Processing Systems 37: Datasets and Benchmarks Track. Red Hook, NY: Curran Associates, 2024.

\bibitem{ref18}
YEH C, CHANG Y M, CHIU W C, et al. T2Vs meet VLMs: A scalable multimodal dataset for visual harmfulness recognition[C]//Advances in Neural Information Processing Systems 37: Datasets and Benchmarks Track. Red Hook, NY: Curran Associates, 2024.

\bibitem{ref19}
RUNWAY. Stable Diffusion v1-5 model card[EB/OL]. [2026-04-24]. \url{https://huggingface.co/runwayml/stable-diffusion-v1-5}.

\bibitem{ref20}
ALI-VILAB. Text-to-video-ms-1.7b model card[EB/OL]. [2026-04-24]. \url{https://huggingface.co/ali-vilab/text-to-video-ms-1.7b}.

\bibitem{ref21}
KHAN A A, LAGHARI A A, INAM S A, et al. A survey on multimedia-enabled deepfake detection: state-of-the-art tools and techniques, emerging trends, current challenges \& limitations, and future directions[J]. Discover Computing, 2025, 28: 48.

\bibitem{ref22}
VERDOLIVA L. Media forensics and deepfakes: an overview[J]. IEEE Journal of Selected Topics in Signal Processing, 2020, 14(5): 910-932.

\end{thebibliography}
